---
title: "Toy example"
author: "Luyang"
date: "2023-10-03"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### load data
```{r}
X = as.matrix(read.delim("input_X.txt", sep = ",",row.names=1))
Y = as.matrix(read.csv("input_Y.txt", sep = ",",row.names=1))

source("../code/R/utils.R")
```



### selection of $X$

In this step, we implement the first stage in the MultiCOP algorithm to select the variables in $X$. In COP step, we employ the cross-validation procedure to select the threshold $c_e$ and $c_d$. The pool of possible $c_e$ is set as $\left\{\chi_{0.90, K}^2, \chi_{0.95 , K}^2, \chi_{0.99 , K}^2\right\}$, and the associated pool of $c_d$ is set as $\left\{\chi_{0.85, K}^2, \chi_{0.90 , K}^2, \chi_{0.95 , K}^2\right\}$. We then select $K$ from from 1 to 6 according to G information criterion.

```{r}
my.range=100; m=100
alpha.in.list = c(0.85,0.90,0.95)
alpha.out.list = c(0.80, 0.85, 0.90) 
scalar.Y = scalar(Y, m=m)
result.X = lapply(1:m, function(i){suppressWarnings(step.multicop.x(i))})
X_sub = select.idx(result.X)
cat("The selected subset in X: ", X_sub, '\n')
```


### selection of $Y$

In this step, we implement the second stage in the MultiCOP algorithm to select the variables in $Y$.

```{r}
X.selected = X[,as.numeric(X_sub)]
scalar.X = scalar(X.selected, m)
result.Y = lapply(1:m, function(i){suppressWarnings(step.multicop.y(i))})
Y_sub = select.idx(result.Y)
cat("The selected subset in Y: ", Y_sub, '\n')

```










