---
title: "Toy example"
author: "Luyang"
date: "2023-10-03"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### load data
```{r}
X = read.csv("input_X.txt")
Y = read.csv("input_Y.txt")

source("../R/utils.R")
```


### selection of hyperparameters $c_e$, $c_d$, and $K$

In this step, we employ the cross-validation procedure to select the threshold $c_e$ and $c_d$. The pool of possible $c_e$ is set as xxxxxxxxxxxx, and the associated pool of $c_d$ is set as xxxxxxxxxxxx. We then select $K$ from a pool of xxxxxxxxxxxxx according to G information criterion.

```{r}
# alpha.in = 0.95;alpha.out = 0.90;my.range=100;m=1000





```


```{r}
cat(paste0("The selected c_e is: ", alpha.in), '\n')
cat(paste0("The selected c_d is: ", alpha.in), '\n')
cat(paste0("The selected K is: ", alpha.in), '\n')
```



### selection of $X$

In this step, we implement the first stage in the MultiCOP algorithm to select the variables in $X$.

```{r}





```


```{r}
cat(paste0("The selected subset in X: ", X_sub), '\n')
```



### selection of $Y$

In this step, we implement the second stage in the MultiCOP algorithm to select the variables in $Y$.

```{r}






```


```{r}
cat(paste0("The selected subset in Y: ", Y_sub), '\n')
```





